### 2015-09-10 paper.tex
Recalculate Reynolds number table

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_c$ at $\lambda = 3$ \\ 
\hline 
0.2 & $2.2 \times 10^5$ & $4.0 \times 10^4$ \\ 
0.4 & $4.3 \times 10^5$ & $8.0 \times 10^4$ \\ 
0.6 & $6.5 \times 10^5$ & $1.2 \times 10^5$ \\ 
0.8 & $8.6 \times 10^5$ & $1.6 \times 10^5$ \\ 
1.0 & $1.1 \times 10^6$ & $2.0 \times 10^5$ \\ 
1.2 & $1.3 \times 10^6$ & $2.4 \times 10^5$ \\ 
1.4 & $1.5 \times 10^6$ & $2.8 \times 10^5$ \\
\end{tabular} 
\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate blade 
chord Reynolds numbers corresponding to tow speeds.} \label{tab:re}
\end{table}

\todo[inline]{Check which chord length was used to calculate $Re_c$, and
recalculate using $\lambda=3.1$.}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_{c_\mathrm{tip}}$ & $Re_{c_\mathrm{root}}$ & $Re_{c_\mathrm{ave}}$\\ 
\hline 
0.4 & $4.3 \times 10^5$ & $5.0 \times 10^4$ & $8.3 \times 10^4$ & $6.6 \times 10^4$ \\ 
0.6 & $6.5 \times 10^5$ & $7.4 \times 10^4$ & $1.2 \times 10^5$ & $9.9 \times 10^4$ \\ 
0.8 & $8.6 \times 10^5$ & $9.9 \times 10^4$ & $1.7 \times 10^5$ & $1.3 \times 10^5$ \\ 
1.0 & $1.1 \times 10^6$ & $1.2 \times 10^5$ & $2.1 \times 10^5$ & $1.7 \times 10^5$ \\ 
1.2 & $1.3 \times 10^6$ & $1.5 \times 10^5$ & $2.5 \times 10^5$ & $2.0 \times 10^5$ \\ 
\end{tabular}

\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate blade
    chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ corresponding to various
    tow speeds at $\lambda=3.1$.}

\label{tab:re}
\end{table}
